Evaluating the Supportive Effect of Feature Selection Methods on Machine Learning Models in Monitoring Forest Health Using Hyperspectral Remote Sensing Data

### 2020-04-07 docs/00-manuscripts/ieee/ieee-manuscript.tex
A.B. review: rephrase disc: algor diffs

We were a bit surprised about the performances of the penalized methods lasso and ridge.
The former was not able to achieve an error below 45.96 RMSE across any dataset while ridge came at least somewhat close to RF and XGBoost for some feature sets.
However, there were also three instances (VI, NRI-VI, HR-NRI-VI) for which the error of the fitted ridge model was out of bounds.
We cannot preclude possible mistakes on our side when optimizing the penalization terms of the penalized learners.

>>>>

We were a bit surprised about the performances of the penalized methods lasso and ridge.
The former was not able to achieve an RMSE below 46.0 p.p. across any feature set while ridge came at least somewhat close to RF and XGBoost for some feature sets.
However, there were also three settings (VI, NRI-VI, HR-NRI-VI) for which the RMSE of the ridge model was out of bounds.
That said, we cannot preclude possible mistakes on our side when optimizing the penalization terms of the penalized learners.
